% !TEX root = ../Dissertation-vLautz.tex

\chapter*{Acknowledgments}
\doublespacing
This thesis could not have been done without the help of many colleagues, friends, and family, who have supported me throughout the last years. 

First of all, I want to thank Felix Blankenburg for all his time, guidance and the fact that he created such a nice atmosphere to do science in. My gratitude goes to Mark Stokes, for being such an approachable supervisor, always taking the time to have in-depth discussions, and believing in me. I also want to thank John-Dylan Haynes and Philipp Sterzer for having an open ear and guiding me especially in the beginning of this PhD.

Many thanks to my colleagues, both in Berlin at the NNU and in Oxford at OHBA. Without your day-to-day discussions, incredible support and overall good vibes, the last few years would not have been half the fun.
Additionally, I want to thank the MEG team in Bennewitz and the Haus 6 residents for all their help.

I am grateful to Leonie, my family, and the gladiators for always being there for me, supporting me through the ups and downs, and always having my back.

Finally, I want to recognize all the institutions that have funded this research. First of all, the Bernstein Center, who beyond giving me financial support has introduced me to a dynamic and interactive research community. Many thanks also to the Oxford Centre for Human Brain Activity, the Studienstiftung des Deutschen Volkes, the DAAD, the Ernst-Reuter Gesellschaft, the Club der Ehemaligen, and the Wikimedia foundation. 

Thank you!
