% !TEX root = ../Dissertation-vonLautz.tex

\chapter{General Discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the research summarized in the previous section, we gained new insights into the role of neural oscillations ascribed to cognitive functions, especially working memory modulated beta and gamma, decision-related beta power and the supramodal nature of the CPP for tracking decisions.

In the first study, we were able to uncover previously hypothesized but never demonstrated modulations of prefrontal gamma and parietal beta power by vibrotactile frequencies held in working memory. Most interestingly, the parietal beta modulations could be source localized to the IPS, an area known to be involved in numerosity processing. These results indicate that a frontoparietal network underlies working memory that employs beta and gamma oscillations in a mechanistic fashion.

The second study encompassed six EEG experiments, whose analysis consistently showed a CPP that accumulated during decision making. With respect to the second stimulus, we observed a scaling of the CPP, first by the subsequent choice and later by trial difficulty, which we relate to confidence. In addition, we found a correlation between choice-related beta and the CPP, suggesting common codes during decision processing. Our findings point to a role of the CPP that goes beyond signaling the status of a DV and insinuate that such a role is related to the decision outcome.

In the most recent experiment, we showed that the functional roles attributed to beta oscillations in the tactile task hold up in a visual variant, indicating a general, supramodal mechanism. Similarly, we demonstrated that non-lateralized choice-dependent beta can also account for decisions when using RDM stimuli. In addition, both stimulus- and response-locked CPPs reflected the tracking of a decision variable during a comparison task that was informed by working memory. This is of particular note, because there was no relationship of the CPP during RDM perception, suggesting independence from sensory processes. Finally, the CPP scaled with subjectively perceived difficulty at the time of response, which further indicates that the CPP incorporates confidence signals.

\section{Unifying accounts of prefrontal beta band oscillations during working memory}

All experiments reviewed here replicated the finding that beta band power from IFG is parametrically modulated by abstract quantitative information (vibrotactile frequency or RDM coherence) held in working memory during a short interval between two stimuli. \textcite{Spitzer2010} had identified this effect at 20-25 Hz with EEG during a similar vibrotactile SFC task. Interestingly, when we used a visual variant of the task, but the same EEG equipment as these authors, the effect was surprisingly similar at 18-26 Hz, however, was found significantly higher (30-35 Hz) in MEG recordings on almost the same vibrotactile task. Because in EEG the skull acts as a low-pass filter \parencite{Pfurtscheller1975} and the observed effect may be an epiphenomenon of averaging further temporally smeared beta bursts, it is quite possible that the prefrontal oscillations even extend into the gamma range. Recent monkey recordings appear to concur with a representation in higher beta oscillations, with a medial premotor beta peak above 25 Hz \parencite{Haegens2017}. This may particularly important, as lower beta modulations (13-20 Hz) occur jointly with alpha \parencite{Hanslmayr2009} and decrease in task-relevant areas while higher beta-band rhythms (20-35) mirror gamma and increase with engagement \parencite{Tallon-Baudry1998}. It may therefore be necessary, in the future, to separate lower beta activity more clearly from higher beta oscillations to avoid grouping them in one beta band.

Our findings in the prefrontal cortex were clearly in the upper beta band and appeared to be related to active processing rather than inhibitory in nature. Enhanced beta has been hypothesized to signal the “status quo” of maintaining the current sensorimotor or cognitive state \parencite{Engel2010}. However, our findings go beyond overall changes. We provide evidence that beta oscillations hold information about the content (vibrotactile frequency or RDM coherence) of working memory on a given trial, joining a growing body of evidence for such a role \parencite{Spitzer2010,Spitzer2011,Wimmer2016}. This type of feature specific activity has also been found in neuronal spiking and high frequency LFPs \parencite{Pesaran2002,Romo1999,Nieder2003} and has been studied extensively with fMRI \parencite{Christophel2012,Christophel2017,Uluc2018,Wu2018}. Yet, it remains unclear how neural activity measured as spike firing rates and BOLD signals relate to the previously observed EEG beta band oscillations. In particular,  it is unknown, whether beta activity correlates positively or negatively with these activity measurements \parencite{Spitzer2017}. Upper beta band oscillations are likely to correspond closer to those in gamma, who have been associated with higher spike rates and increases in BOLD, while low beta may be associated negatively with activity, corresponding to alpha \parencite{Michels2010,Hanslmayr2011}. However, it is also possible that beta is neither associated with activity increases nor decreases, as observed in some studies \parencite{Rule2017, Whittingstall2009}. Therefore our findings with MEG are of particular note, because we demonstrated that both high prefrontal and low parietal beta were associated with the abstract magnitudes held in working memory in the same fashion. We did not, however, observe overall changes, further underlining that beta fulfills a content-specific role. I therefore suspect that the functional role of beta is not directly related to overall spiking/BOLD activity increases as has been observed in gamma, but reflects the updating of content \parencite{Spitzer2017}.

\section{Diverging findings with MEG and EEG}

One major difference between our MEG recordings and previous EEG studies was that we observed parametric changes in gamma spectral power by the to-be-maintained frequency $f1$. One explanation why parametric WM in high frequency gamma oscillations was not detected in the large amount of previous vibrotactile EEG studies \parencite{Herding2016,Spitzer2010,Spitzer2014,Spitzer2011,Spitzer2012} is the previously mentioned nature of the human skull to act as a low-pass filter \parencite{Pfurtscheller1975}. Specifically, EEG and MEG can exhibit distinct frequency versus power relationships in high frequencies, because the capacitive properties of the extracellular medium, i.e. skin and scalp muscle artefacts, distort the EEG, but not the MEG signal \parencite{Buzsaki2012,Dehghani2010,Demanuele2007}. In addition, we used a multitaper approach based on Slepian sequences with a fixed window of 200 ms in the MEG study compared to a window of 400 ms in previous EEG recordings. This shorter time window results in less smoothing in the time domain, which gives rougher estimates, but may have provided us with the possibility to detect more short-lived effects. Because of these differences, we also used the shorter window for exploratory analysis in more recent experiments, for example study 3, resulting in the same negative gamma modulation by the abstract quantity held in working memory as observed with MEG. For prospective WM studies or an eventual meta-analysis of the present findings I therefore also recommend trying out a short window for multitaper analysis of higher frequencies.

In addition to gamma, the MEG recordings differed from EEG recordings in one more area: the IPS. We found that low beta band power (10-20) from this area was parametrically modulated by the abstract quantity retained in WM. There are two methodological reasons that could account for why we detected this modulation with MEG and not EEG \parencite[cf.][]{Spitzer2014}. One, MEG has a higher signal-to-noise ratio for shallow sources \parencite{Goldenholz2009}. Two, MEG is more sensitive to sulcal than gyral sources, because it is blind to radial dipoles, biasing source analysis in favor of sulcal sources \parencite{Ahlfors2010}. However, while unexpected from the previous EEG literature, the involvement of the IPS in quantity processing was not wholly surprising. Concurrent to our research, fMRI studies found a role of the IPS for vibrotactile, visual, and auditory frequency maintenance \parencite{Uluc2018,Wu2018}. Moreover, similar to the abstract stimuli we employ, tasks using concrete numbers have found a direct link between multivariate BOLD-responses in the IPS and quantity \parencite{Eger2009}. This finding builds upon a body of work with nonhuman primates that has revealed a crucial involvement of intraparietal regions for the encoding of quantitative features that are ordered along a continuum \parencite{Jacob2012,Nieder2016}, including supramodal frequency \parencite{Vergara2016}. Furthermore, the IPS has been well-established as a hub for working memory in junction with the prefrontal cortex in studies on capacity limits and appears to be essential for short term object retention \parencite{Todd2004,Todd2005,Vogel2004,Xu2006}. Therefore, a role of the IPS in conjunction with the PFC has been well-established, yet it remains unclear what role beta band oscillations at low frequencies contribute to working memory in this area. In particular, the low beta we observed with MEG includes frequencies associated with the mu rhythm \parencite{Chatrian1959,Gastaut1954}, whose functional role has been viewed as alpha-like suppression for somatosensation\footnote{Note that there is a different view on mu as a correlate of the mirror neuron system: \footcite{Naeem2012,Pineda2005}}. Contrary to this interpretation, we did not observe overall ERD/ERS, but a parametric modulation of lower beta/mu power by the content held in working memory. It is therefore unlikely that the observed effect reflects a generic inhibition or gating mechanism. One possibility is that the inhibition is content specific, explicitly because another stimulus is being presented subsequently that is sure to be different in vibrotactile frequency. Thus, the stimulus frequency held in working memory could be inhibited. However, the parametric modulation of IPS did not extend to the time of f2 stimulation, rendering this interpretation unlikely. Similarly, the mu rhythm is associated with attention \parencite{Anderson2011} and it is possible that participants paid more attention to higher frequencies. This is unlikely for two reasons. First, we did not observe behavioral effects in this direction, and second, prefrontal gamma band and occipital alpha would be expected to be similarly modulated, which we also did not observe (in this direction). Therefore, a role of the IPS for numerosity processing and working memory is well-established and it appears that our observations are difficult to reconcile with the inhibitory nature of low frequencies. I speculate that our observations reflect an active maintenance mechanism, possibly interacting with prefrontal gamma.

\section{A frontoparietal beta-gamma code}
One idea could be that the IPS maintains the information and is top-down controlled by prefrontal areas in a periodic replay based upon interactions of beta and gamma. This idea is analogous to computational modeling of neuronal firing patterns in animals proposing that working memory arises from periodically reactivating the content held in working memory, guided by gamma and theta oscillations \parencite{Fuentemilla2010,Jensen2005,Lisman1999,Lisman1995}. This concept likely extends beyond the theta-related hippocampus to other areas and frequency bands \parencite{Lundqvist2016,Mongillo2008} and could be modulated on short time scales by attention \parencite{Awh1998}. Moreover, there is evidence of PFC-PPC coupling in the beta and delta bands, with delta reflecting task-irrelevant stimulus dimensions and beta only those immediately relevant \parencite{Antzoulatos2016}. Yet so far, a gamma-beta relationship has only been shown within the prefrontal cortex \parencite{Lundqvist2016} and not across frontoparietal areas. 
However, this same idea may serve to explain the pattern of concurrent high beta band increases and gamma decreases with the abstract quantity held in working memory I observed both with MEG and EEG in separate tactile and visual studies. \textcite{Lundqvist2016} observed brief gamma (45-100 Hz) and beta (20-35 Hz) bursts during single cell and LFP recordings of monkeys performing a working memory task. The gamma bursts increased during encoding and recall, while the beta bursts reflected a default network state that was interrupted by gamma. My findings could be an epiphenomenon of such a coding scheme, but reflected in mean power differences due to averaging over trials smoothing out individual bursts. Further analysis using SFC tasks in humans should concentrate on understanding the single trial dynamics. Because signal to noise ratios in M/EEG can be low, this has proven difficult in the past. One avenue may lie in observing the cross-frequency coupling, both in power changes and rhythmicity \parencite{Fransen2015}. Another promising method to investigate the network configuration of oscillations may lie in the extraction of frequency-specific timecourses
with high temporal resolution \parencite{Vidaurre2016,Vidaurre2018}. However, perhaps more importantly, mechanistic accounts of PPC-PFC function will have to evaluate whether gamma from superficial cortical layers and beta from deep layers also enact a similar relationship in other cortical areas \parencite{Miller2018,Christophel2017}.

Under close examination this idea of a dynamic frontoparietal beta-gamma code speaks against working memory as a function grounded in sustained prefrontal firing rates \parencite{Funahashi1989,Fuster1971,Goldman-Rakic1995,Pasternak2005}. Studies demonstrating continuous delay activity have relied heavily on trial and spike averaging, convoluting more complex single trial dynamics \parencite{Rainer2002,Shafi2007}. Indeed, similar to the previously mentioned beta-gamma patterns \parencite{Lundqvist2016}, most neurons are variable in their spiking behavior in both timing and duration throughout retention intervals and show dynamic coding schemes transitioning between coding states \parencite{Cromer2010,Durstewitz2006,Spaak2017,Stokes2013}. Moreover, recent neuroimaging studies suggest that working memory can be ‘activity silent’ when stimuli are unattended or irrelevant for current task demands \parencite{Lewis-Peacock2012,Stokes2015,Wolff2015,Wolff2017}. While the role of such silent states is currently under high-level debate \parencite{Christophel2018}, evidence converges on the idea that working memory does not rely on sustained prefrontal firing as a solitary mechanism \parencite{Lundqvist2018,Spaak2017}. My data agrees with this notion. First, contrary to \textcite{Haegens2010} we did not observe an overall increase of gamma power during working memory as would be expected from sustained firing, while EEG findings for alpha and beta were replicated. Second, irrespective of whether gamma power changes reflected bursting, the observed changes in gamma were in a finite time window and not sustained throughout the whole interval. Third, while single-trial dynamics remain unclear, the pattern of gamma decrease with concurrent beta increase in PFC and PPC hint at a relationship between these frequency bands for working memory. 
The key to a unifying explanation for these effects may be provided by a very recent monkey study: \textcite{Lundqvist2018} found that gamma increased, and beta decreased shortly before items in working memory had to be used for decision making, while gamma decreased and beta increased when stimuli were not needed anymore. The authors interpret this as beta oscillations regulating control over gamma and working memory, a view summarily fitting to our results and recent investigations into the role of beta “beyond the status quo” \parencite{Haegens2017,Ludwig2018,Lundqvist2018,Spitzer2017}. 
In this view, beta oscillations provide a mechanism to guide neural ensembles for the (re-)activation of maintained information. This builds on the observation that beta facilitates top-down driven communication across long distances and cortical areas \parencite{Antzoulatos2016,Arnal2012,Bastos2015,Engel2010,Michalareas2016,Sejnowski2006,Siegel2012,Varela2001,Wang2010}, but beyond static maintenance can be characterized as a dynamic mechanism that can facilitate content-specific encoding and read-out by “waking up” in the form of short temporal bursts \parencite{Fries2015,Jones2016,Lundqvist2018,Spitzer2017}. The question remains however, whether beta facilitates information “wake up” over long range connections, e.g. from sensory areas or if it is a mechanism of central processing in the prefrontal cortex. This is particularly interesting, because during visual and tactile tasks I have found consistent parametric modulations of beta oscillations in the PFC while none from sensory areas.
\section{Distributed codes or central working memory?}
While we observed working memory related activity consistently only in the prefrontal cortex, recent accounts also focus on a role for parietal and sensory cortices \parencite{Bettencourt2015,Christophel2017,Sreenivasan2014,Xu2015}. In particular, studies using MVPA on fMRI recordings during the maintenance of precise visual details could reliably decode stimulus content from sensory cortices, yet failed in frontal areas \parencite{Christophel2012,Emrich2013,Riggall2012}. When operationalizing the retention of vibrotactile frequencies however, fMRI has revealed multivariate parametric codes in prefrontal and sensory areas \parencite{Schmidt2017,Wu2018}. Thus, multiple avenues of research into working memory have found very distinct regions to be involved - how can these findings be consolidated?
One idea is that the locus of working memory follows the processing in terms of the cortical hierarchy \parencite{Eriksson2015,Fuster2012,Zimmer2008}. Moreover, \textcite{Christophel2017} postulate that for one, all cortical regions can maintain information over a short period of time. And for two, that the nature of the task dictates the relevant region in the cortical hierarchy depending on low level sensory features and the level of abstraction of the to-be-remembered stimulus. With such an interpretation of previous results, the areas involved in working memory can range from the prefrontal cortex for abstract, complex stimuli to low-level features in primary sensory cortices. Contrary to early MVPA fMRI studies tasking volunteers to remember low-level sensory details, we used abstract magnitude information, either in the form of vibrotactile flutters or the perceived coherence of a random dot kinematogram. Therefore, it is expected from this account that the representation in our studies materializes in areas such as the PFC and higher-order parietal regions, which process abstract, supramodal information. Furthermore, this idea may serve to explain the beta band modulation in motor areas before pressing a button we observed in terms of active perceptual memory. In this case, the motor-specific areas would also maintain information over a short period of time relevant to their place in the cortical hierarchy: the motor code for a subsequent button press.

\section{Beta band during decision making}
Beyond a role for working memory, we found an involvement of premotor beta band activity during decision making in a visual task and used previous findings of decision-related beta in tactile tasks to establish an association with concurrent centroparietal signals. Unfortunately, due to technical difficulties with both the vibrotactile stimulation device and the eye-tracking system, an analysis of our MEG data set in relation to decision making was unsuccessful \parencite[cf.][]{Chandler2015}. This is particularly lamentably, because \textcite{Donner2007} used MEG in a RDM task and found that beta band activity predicted the accuracy and not the content of upcoming perceptual reports, for which we found no evidence with EEG.

The modulation of upper beta band power by subjects’ choices we observed in sequential comparison tasks is in accord with choice signals in monkey LFPs \parencite{Haegens2011} in frequency, timing and cross-species location. Moreover, the increase in beta power for choices $S2>S1$ vs. $S2<S1$ follows the same direction common to all previous studies \parencite{Haegens2011,Herding2016,Herding2017,Ludwig2018}. Remarkably, when comparing patterns of visual (study 3, figure 4) and tactile studies \parencite[][figure 4]{Herding2016} the time-frequency maps and topographies appear incredibly similar even though stimulus processing relied on distinct sensory modalities and the tasks had divergent timings.

This similarity between tactile and visual decision making indicates that the underlying process is supramodal and might indeed depend on the motor output rather than the sensory domain as predicted from the intentional framework of decision making \parencite{Shadlen2008}. Further evidence stems from data used in study 2, experiments 1 and 2. Published also as Herding et al. (2016, 2017),
%\textcite{Herding2016,Herding2017}
 this data demonstrates that depending on the response modality, the choice-selective beta band modulation can be source localized either to the premotor cortex for button press or the FEF for saccade responses. While these tasks used essentially the same sequential frequency comparison, we can now add that also in the comparison of sequentially sampled RDM stimuli the decision-related beta band modulation can be observed. This is particularly interesting, because during motor processing the beta frequency band does not solely represent motor preparation, as historically thought \parencite{Pfurtscheller1981}. Indeed, when participants responded with either their left or right hand, lateralized beta band power over contralateral MI scaled with the process of accumulating evidence for a decision, tracking the evolving decision variable \parencite{Donner2009,OConnell2012}. In our recordings with button-press responses, we used the right index and middle fingers, which in addition were counterbalanced across volunteers, eliminating the possibility that contralateral sensorimotor beta band modulations accounted for choice-dependent beta exclusively. Moreover, because in study 3 we used a visual task and found almost identical results, we can separate such decision-beta from the beta oscillations observed during somatosensory perception. If this modulation is indeed independent from perception and is related to the choice information, then we should only be able to find it if a response mapping is provided. Therefore, in study 2, experiments 3+4, also published as \textcite{Ludwig2018}, participants were only provided with the response mapping after a short delay and had to transform the decision information onto a colour code. Interestingly, in those trials where responses could not be immediately transformed into motor commands the beta band was also similarly modulated, but in posterior parietal cortex, not premotor areas. Taken together with our visual and tactile experiments employing direct mappings, this implies that the way we respond determines where in the sensorimotor hierarchy the decision is processed and supports an intentional framework \parencite{Shadlen2008}. Furthermore, our findings indicate that the beta band reflects the categorical, abstract content of a decision, even in the absence of a motor plan. This is particularly interesting, because also broadband centroparietal signals (CPP) have been theorized to reflect the closely related process of accumulating evidence.

\section{Common ground for CPP and decision beta}
Both the premotor beta oscillations and the CPP we observed are candidate signals to reflect large-scale neural ensembles expressing the repeated sequential sampling and integration in sensorimotor neurons observed in studies with nonhuman primates \parencite{Gold2007,Hanks2017,Kelly2015,Spitzer2017}. In particular, they correspond well to studies focusing on the role of the PPC for decision formation. As introduced earlier, the LIP is closely connected  to the accumulation of motion information from direction-selective neurons in MT, but also with frontal areas such as the FEF \parencite{Ding2012}. Notably, the LIP and FEF can both exhibit ramping up of neural activity and can reach a fixed level prior to saccade responses \parencite{Ding2010,Ding2012,Hanes1996,Roitman2002}. While the function of single neurons in these areas has been studied extensively, the precise role of the large-scale signals recorded with EEG, decision beta and CPP, remains uncertain.

The closest link between monkey and our human studies might be found between my third study and \textcite{Wimmer2016}. They recorded LFPs from monkey lateral prefrontal cortex during a sequential comparison task of the speed and direction of two RDM patches. During stimulus perception beta power was reduced, but theta and gamma increased. Throughout the working memory interval beta power encoded the task-relevant $S1$ feature, matching our findings in visual and tactile recordings. After $S2$ onset broadband LFP activity tracked the difference between $S1$ and $S2$ with an early sensory-related component reflecting the stimulus difference and a later component associated with the behavioural decision build-up. This is remarkably similar to our findings concerning the CPP, but in a wholly different area. However, the lPFC is very well-connected with the PPC \parencite{Cole2010} and my own findings add to a well-established relationship between these areas \parencite{Cole2013,Cole2007,Duncan2010,Muhle-Karbe2017,Nieder2016}. These results, in conjunction with ours, indicate that during cognitive tasks a network of prefrontal and parietal areas transition dynamically between neural coding states in a variety of frequency bands rather than one type of oscillation or broadband signal underlying perceptual decision making.

 The coupling between CPP and choice-related beta in our findings, however, indicates that broadband signals and the beta band fulfil very related roles. I speculate that the CPP reflects the absolute value of a DV - maybe confidence - in an accumulation-to-bound manner, while the choice-related beta band serves to communicate the result of this process, continuously over time as is crucial for response preparation. This serves to explain, why choice-related beta appears so early in all our recordings (studies 2 \& 3), about 150 ms after onset of the second stimulus, and disappears long before motor action is taken. This observation indicates that choice-related beta is strongest, when the CPP accumulates the most and the most updating of information is necessary \parencite{Twomey2015}. Moreover, this explains also why premotor beta band modulations could only be observed when the response modality was clear \parencite{Ludwig2018}: the information was retained in the PPC till responses could be made. If the choice-related beta was exclusively related to response preparation, we would have observed such a modulation before subjects responded, regardless. However, further research into the beta band – CPP relationship will be necessary, to which I want to point in the next section.
 
\section{Future Avenues}

The present studies call for follow-up experiments. 
First, similar to our task design in study 1 \parencite[see attached study: ][]{VonLautz2017}, it may be interesting to know where choice-beta will originate if there is a delay before responding and the response modality (button press / saccade) is either known or unknown on a trial-by-trial basis. I would hypothesize that in trials with unknown response modality beta band modulations source localize to the PPC, while in trials where subjects know how to answer, this effect originates from premotor areas or FEF.

Second, we observed a scaling of the CPP with subjectively perceived stimulus differences and related these changes to statistical decision confidence. A crucial next step will be to record actual ratings of confidence on single trials to uncover how confidence interacts with the accumulation of evidence tracked by the CPP. In particular, it remains unclear whether at the time of response a fixed threshold bound is reached or if the signal is modulated by confidence \parencite{Gherman2015,Kelly2013,Kelly2015,Philiastides2014,Twomey2016}. For example, our recordings in study 3 demonstrate that the CPP builds-up as expected from an accumulation process, but is scaled by trial difficulty at the time of response. A drift-diffusion model with non-collapsing bounds would have predicted that a fixed threshold of CPP amplitude is reached independent of trial difficulty as observed in similar recordings \parencite{Kelly2013}. For future mechanistic explanations and the large body of modelling work on such decision processes we should identify if confidence signals, e.g. from the ventral striatum as observed with fMRI \parencite{Hebart2016}, are either mixed with or alternatively directly influence the CPP. 

Third, it will be important to investigate gamma oscillations in this task more thoroughly, because – as previously discussed – the beta band is theorized to reflect the re-activation of content \parencite{Spitzer2017} and might reflect a maintenance state that is interrupted by short gamma bursts \parencite{Lundqvist2018,Lundqvist2016}. Because re-activation of content may only be necessary across timespans above one second, it will be important to investigate gamma during a longer WM interval. Moreover, gamma has not been investigated during decision making in the SFC task and a possible relationship with the CPP should be investigated. MEG however, appears unsuited to detect a centro-parietal field\footnote{It would be called 'field', and not 'potential' because flux is measured in terms of space}, and previous MEG studies were not able to find such a parietal signal \parencite[e.g.,][]{Donner2009}. One avenue would be to record concurrent M/EEG and use both signals to detect high-frequency gamma and the CPP. In addition, recent developments based on the Hidden Markov Model  have been used to identify fast transient states in M/EEG data \parencite{Vidaurre2018,Vidaurre2016}, and could be a promising method to characterize such a mechanism. 

\section{General Summary}
As climate change leads to ever higher temperatures \parencite{Parmesan2003}, buying good quality watermelons will become more important. So, what can we say about the neural basis of finding the right melon? First, when we feel the watermelon, the power of neural oscillations in the alpha band increase over task-irrelevant visual areas. Concurrently, low beta (mu) oscillations increase over the ipsilateral hemisphere of the hand doing the feeling, while decreasing over the contralateral. Then, while we keep how the watermelon felt in memory before selecting another to test, beta band power increases with this abstract quantity, while gamma decreases. Finally, before we point to the watermelon we want to buy, broadband centroparietal signals characterize the process of accumulating evidence for one melon or the other while beta band activity from premotor areas reflects our choice. These large-scale neural oscillations reflect the dynamic, fast-paced changes in single neurons and neuronal populations that unite their rhythms, making them detectable with neuroimaging methods from outside the human skull. This suggests that the brain uses neural oscillations to communicate information between different areas and that the more we understand about these rhythms the better we can understand the language the brain uses.